---
title: "project"
author: "Thanh Dung"
date: "2022-11-09"
output: html_document
---

```{r setup}
library(tidyverse)
library(tm)
library(caret)
library(wordcloud)
library(e1071)
```

## Data Understanding

```{r}
rawDF <- split
View(rawDF)
```

## Data preparation
# remove first id variable
```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

#checking the counts and proportions of the outcomes (variable Category)
```{r}
cntCat <- table(cleanDF$class)
propCat <- round(prop.table(cntCat) * 100 , digits = 1)

cntCat
propCat
```

#setting factor type for the variable
```{r}
cleanDF$class <- factor(cleanDF$class, levels = c("Crime","Culture", "Entertainment", "Politics", "Business","Lifestyle","Food", "Health", "One-one-two", "Weird", "Tech","Nature","Art", "Sports", "Science", "Innovation", "Sponsored", "Content" ), labels = c("Not Interested","Interested", "Interested", "Interested", "Interested","Interested","Interested", "Interested", "Not Interested", "Interested", "Interested","Interested","Not Interested", "Not Interested", "Interested", "Interested", "Not Interested", "Not Interested" )) %>% relevel ("Not Interested")
head(cleanDF, 10)
```

# visually inspect the data by creating wordclouds
```{r}
Interested <- cleanDF %>% filter(class == "Interested")
NotInterested <- cleanDF %>% filter(class == "Not Interested")

wordcloud(Interested$content, max.words = 20, scale = c(4, 0.8), colors= c("indianred1","indianred2","indianred3","indianred"))
wordcloud(NotInterested$content, max.words = 20, scale = c(4, 0.8), colors= c("lightsteelblue1","lightsteelblue2","lightsteelblue3","lightsteelblue"))
```

```{r}
rawCorpus <- Corpus(VectorSource(cleanDF$content))
inspect(rawCorpus[1:3])
```

# remove numbers, punctuation, unuseful words, and change to lower case
```{r}
cleanCorpus <- rawCorpus %>% 
  tm_map(tolower) %>% 
  tm_map(removeNumbers) %>% 
  tm_map(removeWords, stopwords()) %>% 
  tm_map(removePunctuation) %>% 
  tm_map(stripWhitespace)
```

# inspect the corpus
```{r}
tibble(Raw = rawCorpus$content[1:3], Clean = cleanCorpus$content[1:3])
```

# transform to matrix
```{r}
cleanDTM <- cleanCorpus %>% DocumentTermMatrix
inspect(cleanDTM)
```

# Create split indices
```{r}
set.seed(1234)
trainIndex <- createDataPartition(rawDF$class, p = .75, 
                                  list = FALSE, 
                                  times = 1)
head(trainIndex)
```

# Apply split indices to DF
```{r}
trainDF <- cleanDF[trainIndex, ]
testDF <- cleanDF[-trainIndex, ]
```


# Apply split indices to Corpus
```{r}
trainCorpus <- cleanCorpus[trainIndex]
testCorpus <- cleanCorpus[-trainIndex]
```


# Apply split indices to DTM
```{r}
trainDTM <- cleanDTM[trainIndex, ]
testDTM <- cleanDTM[-trainIndex, ]
```

# eliminate words with low frequencies
```{r}
freqWords <- trainDTM %>% findFreqTerms(5)
trainDTM <-  DocumentTermMatrix(trainCorpus, list(dictionary = freqWords))
testDTM <-  DocumentTermMatrix(testCorpus, list(dictionary = freqWords))
```

# transform the counts into a factor -> see whether the word appears in the document or not
```{r}
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) %>% factor(levels = c(0,1), labels = c("No", "Yes"))
}
```

```{r}
nColsDTM <- dim(trainDTM)[2]
trainDTM <- apply(trainDTM, MARGIN = 2, convert_counts)
testDTM <- apply(testDTM, MARGIN = 2, convert_counts)
```

```{r}
head(trainDTM[,1:10])
```


## Modeling
```{r}
nbayesModel <- naiveBayes(trainDTM, trainDF$class, laplace = 1)
```

```{r}
predVec <- predict(nbayesModel, testDTM)
confusionMatrix(predVec, testDF$class, positive = "Interested", dnn = c("Prediction", "True"))
```
